working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods changes

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The species selected (**Table 1**) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae. The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1)[I would explain more the bauty of our nested dessign to ensure close and far distance simultaneously](), heterogeneous traits, low structural flower complexity and fast life cycle. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

>>>>

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**). The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crossed between species allowed us to have multiple different scenarios of both traits and relatedness. Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the different pollination treatments and grow the different species from seeds. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods changes

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The species selected
(\textbf{Table 1}) belonged to three different families, Solanaceae,
Brassicaceae and Convolvulaceae. The criteria of species/family
selection was based on close/distant related species (see phylogenetic
tree for relatedness fig 1)\href{}{I would explain more the bauty of our
nested dessign to ensure close and far distance simultaneously},
heterogeneous traits, low structural flower complexity and fast life
cycle. For the purpose of the experiment all the species where
considered as pollen recipient and as pollen donor (see interaction
matrix, fig 2). Species were watered once or twice per day and
fertilized weekly (NPK 23: 3.95: 14).

>>>>

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The experimental design had
species from three different families: Solanaceae, Brassicaceae and
Convolvulaceae (\textbf{Table 1}). The different species of the study
have different reproductive traits and different degree of relatedness
where the reciprocal crossed between species them allow us to have
multiple different scenarios of both. Moreover, the species selected
have fast life cycle and low structural flower complexity in oprder to
perform the different pollination treatments. For the purpose of the
experiment all the species where considered as pollen recipient and as
pollen donor (see interaction matrix, fig 2). Species were watered once
or twice per day and fertilized weekly (NPK 23: 3.95: 14).
